The Art of Robotics:\\\vspace{0.2em}\huge{Toward A Holistic Approach}

### 2018-07-29 ms-thesis-slides.tex
moving stuff around, switched to Lualatex build
adding slides, ri memes stuff

%!TEX program = xelatex
\documentclass[aspectratio=169]{beamer}

\usepackage{blindtext}

@@

\title{The Art of Robotics:\\\vspace{0.2em}\huge{Towards A Holistic Approach}}
\subtitle{Master of Science in Robotics\\Thesis Defense}
\author{Alexander Volkov Jr.}
\date{July 31, 2018}

@@

	\begin{frame}
		\frametitle{Talk Agenda}
		\begin{enumerate}
			\item Other Things \\ 
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Warm up the crowd with a quick review of some other things I've done.}
			\item The Big Picture \\ 
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Cover the central themes of this talk.}

			\item Bond Graphs, Impedance/Admittance Matching \\
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} An old framework, revived.}

			\item Brushless PMSM Motors \\
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Operating limits, thermal management, liquid cooling.}

			\item Touching Robots \\
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Tactile sensing, whiskers, robot pain.}

			\item Conclusions \\ 
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Review key points and propose some future work.}

			\item Questions \\
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} \emph{``Please clap...''}}
		\end{enumerate}
	\end{frame}

@@

	\section{Other Things}
		\begin{frame}
			\frametitle{Teaching}
			Gelfand Center
		\end{frame}

@@

		\begin{frame}
			\frametitle{Robotics Institute Meme Facebook Page}
			Started the RI's first and only meme page
			Current stats?
			Some meme examples?
		\end{frame}

	\section{The Big Picture}
		\begin{frame}
			\frametitle{}
			\begin{enumerate}
				\item LaTeX is great!
				\item Beamer is easy to use!
				\item Why not?
			\end{enumerate}
		\end{frame}

	\section{Lorem Ipsum}
		\begin{frame}
			\frametitle{Lorem 1}
			\blindtext
		\end{frame}

		\begin{frame}
			\frametitle{Lorem 2}
			\blindtext
		\end{frame}

		\begin{frame}
			\frametitle{Lorem 3}
			\blindtext
		\end{frame}

	\section{Conclusions}
		\begin{frame}
			\frametitle{Closing Thoughts}
			\begin{itemize}
				\item Woo, Beamer!
			\end{itemize}
		\end{frame}

>>>>

%!TEX program = lualatex
\documentclass[aspectratio=169]{beamer}

\usepackage{blindtext}
\usepackage{multimedia}

@@

\title{The Art of Robotics:\\\vspace{0.2em}\huge{Toward A Holistic Approach}}
\subtitle{Master of Science in Robotics\\Thesis Defense}
\author{Alexander Volkov Jr.}
\date{July 31, 2018}

@@

	\begin{frame}
		\frametitle{Talk Agenda}
		\begin{enumerate}
			\setlength{\itemsep}{4mm}
			\item Background
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} How I ended up here.}

			\item Other Things
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Warm up the crowd with a quick review of some other things I've done.}

			\item The Big Picture
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Cover the central themes of this talk.}

			\item A Unifying Framework
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} An old framework, revived.}

			\item Brushless PMSM Motors
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Operating limits, thermal management, liquid cooling.}

			\item Touching Robots
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Tactile sensing, contact modeling, whiskers, robot pain.}

			\item Conclusions
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} Review key points and propose some future work.}

			\item Questions
				\textcolor{AVThesisGrey}{\footnotesize\hspace{1em} \emph{``Please clap...''}}
		\end{enumerate}
	\end{frame}

@@

	\section{Background}
		\begin{frame}
			\frametitle{How I Ended Up Here}

		\end{frame}

	\section{Other Things}
		\begin{frame}
			\frametitle{Teaching with CMU's Gelfand Outreach Center}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=center] (gelfand-logo) at (0.88\textwidth, 0) {\includegraphics[width=5cm]{media/gelfand-logo.jpg}};
			\end{tikzpicture}
			\begin{itemize}
				\item Introduction to Robotics with the Finch Platform
					\begin{itemize}
						\item Each session is 5 days, 3 hrs/day
						\item 4\textsuperscript{th} and 5\textsuperscript{th} graders
						\item 1 session Summer 2017 + 2 sessions Summer 2018
					\end{itemize}
					\vspace{1em}

			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Teaching with CMU's Gelfand Outreach Center}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=center] (gelfand-logo) at (0.88\textwidth, 0) {\includegraphics[width=5cm]{media/gelfand-logo.jpg}};
			\end{tikzpicture}
			\begin{itemize}
				\item Saturday Series LEGO WeDo Robotics
				\begin{itemize}
					\item 3 hour course
					\item 2\textsuperscript{nd} and 3\textsuperscript{rd} graders
					\item 1 session Spring 2018
				\end{itemize}
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Robotics Institute Meme Facebook Page}
			\begin{tikzpicture}[overlay, remember picture]
				\node[anchor=center] (ri-meme-screenshot) at (current page.center) {\includegraphics[width=\textwidth]{media/ri-memes.jpg}};
			\end{tikzpicture}
		\end{frame}

		\begin{frame}
			\frametitle{Robotics Institute Meme Facebook Page}
			\begin{itemize}
				\item Some statistics:
					\begin{itemize}
						\item The RI's first and only meme page
						\item Formed in March 2018
						\item 170 members
						\item 30 memes, 23 original contributions!
					\end{itemize}
			\end{itemize}
	\end{frame}

	\section{The Big Picture}
		\begin{frame}
			\frametitle{Breadth First}
			\begin{enumerate}
				\item 
			\end{enumerate}
		\end{frame}

@@

	\section{A Unifying Framework}
		\begin{frame}
			\frametitle{The Port-Hamiltonian Framework}
			\begin{itemize}
				\item Port-based Analysis
				\item Hamiltonian Dynamics
					\begin{itemize}
						\item 
					\end{itemize}
				\item
			\end{itemize}
		\end{frame}

		\begin{frame}
			\frametitle{Bond Graphs}

		\end{frame}

		\begin{frame}
			\frametitle{Hamiltonian Dynamics}

		\end{frame}

		\begin{frame}
			\frametitle{Putting it All Together}

		\end{frame}

	\section{Brushless PMSM Motors}

		\begin{frame}
			\frametitle{???}
		\end{frame}

	\section{Touching Robots}

		\begin{frame}
			\frametitle{The Most Important Sensory Modality}
		\end{frame}

		\begin{frame}
			\frametitle{Contact Models}
		\end{frame}

		\begin{frame}
			\frametitle{Terminator 2 Got It Right}
			\begin{center}
			\movie[height = 0.6\textwidth, width = 0.8\textwidth,showcontrols]{}{media/terminator2-pain.mp4}
			\end{center}
		\end{frame}

	\section{Closing Thoughts}
		\begin{frame}
			\frametitle{Closing Thoughts}
			\begin{itemize}
				\item Woo, Beamer!
			\end{itemize}
		\end{frame}
